---
title: "2021-10-7-Project-1-Blog"
author: "Aries Zhou"
date: "10/07/2021"
---
```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("_Rmd/2021-10-7-Project-1-Blog.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts/",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Project 1 Backgrounds  

This Project is to access data sets from the One Call API and perform data exploration and graphical summaries. 

Connects to the One Call API.  

The One Call API provides the following weather data for any geographical coordinates:  

 - Current weather  
 - Minute forecast for 1 hour  
 - Hourly forecast for 48 hours  
 - Daily forecast for 7 days  
 - National weather alerts  
 - Historical weather data for the previous 5 days  

These data can be accessed by defining parameters in the URL. I selected 84 data sets by longitudes across the latitude 35.78 (each data is 4.3 longitudes away from each other with the same latitude). I choose a latitude of 35.78 because this is where NC State is located. These small data sets each containing 8 observations of current and future 7 days weather forecasting information are then selected and recombined into a full data set. 

New variables of Wind Status and Area are created and the average daily temperature is calculated for further data summaries. 

The following graphs are used to compare the differences between the land and water/ocean areas across the latitude of 35.78 on Earth.     

 - Histogram for Temperature
 - Boxplot for Temperature
 - Barchart for Wind Status
 - Boxplot for Humidity
 - Scatterplot for Wind Status v.s. Humidity.

#### Findings  

 - Wind status on the land area is more calm while it is more windy over the water area.                                                 
 - The water area tend to have higher average daily temperature in the future 7 days. This is a little surprising since I was expecting windy areas to be cooler.    
 - While both of the temperature and humidity over the water areas are higher in general, the temperature and humidity varies more on the land areas.    
 - There is a slight positive correlation relationship between the temperature and humidity. Warm air tend to hold more vapor than cool air.        


#### Reflections  

The most difficult part of the logic and programming
 Initially, the most difficult part for me is to choose data from the APIs. The massive and diverse data options are overwhelming. For the logic and programming, the data manipulation section was the most difficult part. The datasets from the API came with a complicate structure, which enhanced the difficulty to manipulate them in the wrapper function. 
 
In the future project, I will try to improve the function efficiency in approching the results, such as using the repetition function, lapply or parallel computing instead of for loops. 

#### [Link](https://github.com/ywzhou33/ST558-Project-1.git) to the Github Pages repo and [link](https://github.com/ywzhou33/ywzhou33.github.io.git) to Github Blog repo.  


```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("2021-10-7-Project-1-Blog.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```
