---
title: "ST558 Reflection"
author: "Aries Zhou"
date: "11/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **Reflections**   

I originally thought that data scientist were more focusing on exploring already-exist data, but that was not true. I understand now that data scientist does not care too much about those known; they put more emphasis on prediction about the unknown.   

I will continue using R in the future. After this semester of studying, I further experienced and enjoyed the advantages of R programming. My current thoughts about R are similar to thoughts in the beginning of the semester. R is a such powerful tool that are so flexible and easy to access for data analysis and model prediction. Its diverse database and packages are great resources for my future studying. However, its efficiency improvement is still a big challenge. When facing missive computation, R is quit slow and dose not improve much using parallel computing.  

In this course, I realize that the Rmarkdwon is very useful as digital notebook. I had switched to taking notes using Rmarkdwon and had been using it to generate files for homework in other classes. 


```{r, echo = TRUE, eval = FALSE}
rmarkdown::render("2021-11-29-Reflec-Blog.Rmd", 
                  output_format = "github_document", 
                  output_dir = "../_posts/",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
