---
title: "Programming Background"
author: "Aries Zhou"
date: "9/12/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```

## Backgrounds

In terms of advantages comparing to the other software, I think R is very powerful and flexible since it contains a large range of functions and new methods are easy to implement in the environment. R also has extensive help resources and able to list all possible functions/options when initial tokens are entered. However, it is relatively slower when working on massive datasets, and many of its online functions resources are not credible. 

Other than R, I also like to use SAS. I miss the part that SAS usually produced prettier outputs than R. The plots and outputs produced in R are too plain that look like the style in decades ago. 

I think R is a little harder to begin with, and due to its flexibility in many aspects, there is always something new to explore and learn about.

## Example R Markdown Output.  

```{r iris, echo=FALSE}
plot(iris)
```
```{r, echo = FALSE, eval = FALSE}
rmarkdown::render("2021-9-12-Second-Blog-Post.Rmd", 
                  output_format = "github_document", 
                  output_dir = "_posts",
                  output_options = list(html_preview = FALSE, keep_html=FALSE))
```
